---
title: "Xaringan minimal example"
author: "zgfabian"
output:
  xaringan::moon_reader:
    seal: true
    css: [default, rutgers, rutgers-fonts]
    lib_dir: ./lib
    nature:
      highlightLines: true
      highlightStyle: zenburn
      countIncrementalSlides: false
---
class: inverse

## Aim

In my [previous post](https://zgfabian.github.io/2021-04-28-xaringan-prez/) I tried to show how to deploy a xaringan presentation to a *Jekyll* site hosted on a *github.io* site. The following post is a minimal example of local deployment that is independent of any R IDE. You can execute it from a terminal like:

```{sh, eval = FALSE}
Rscript minimal-example.R
```

However, if you run the script outside Rstudio IDE, than you have to install [pandoc](https://www.pandoc.org) for your OS environment. RStudio is bundled with pandoc, and other dependencies (like javascript and css) are handled by `xaringan` itself.
You can verify pandoc installation from a terminal with:

```{sh, eval = FALSE}
pandoc --version
```

---

## Review of the `minimal-example.R`

### Get `remark.js` with xaringan 

Download `remark.js`. It can be a good idea to pin a specific version.

```{r}
setwd(".")
dir.create("./lib", showWarnings = FALSE)
xaringan::summon_remark(version = "0.14.1", to = "./lib/")
list.files("./lib/")
```

--

### Download or create a minimal Rmarkdown example

```{r}
url <- "https://raw.githubusercontent.com/ZGFabian/zgfabian.github.io/gh-pages/static/xaringan-prez/_minimal-example.rmd"
download.file(url = url, destfile = "minimal-example.rmd")
```

If you would like to create for yourself, you can do it with `file.create()`, `file.edit()` functions.

---

### Render Rmarkdown to HTML and open in a browser

After we got `minimal-example.rmd` to render Rmarkdown to HTML:

```{r, results = "hide"}
rmarkdown::render(input = 'minimal-example.rmd',
                  output_format = 'xaringan::moon_reader',
                  output_file = "minimal-example.html",
                  output_dir = ".",
                  clean = TRUE)
# list.files("./lib/")
```

As you can see with `list.files("./lib/")` command, `render` created some extra folders in `lib` folder. We have two extra folders: "header-attrs-2.8" and "remark-css-0.0.1". It is just a technical note and you don't really have to care about. As a final step we check out our fresh presentation in a browser (firefox in the example):

```{r, eval = FALSE}
options(browser = "firefox") # any browser of your choice
browseURL("minimal-example.html")
```

--

## Demo ends here

